### 2015-07-20 implementation.tex
Name change spack-paper-sc15 -> spack-sc15
clarify unique features.

%!TEX root = paper.tex

@@

\noindent
Spack has the following unique capabilities:
\begin{enumerate}
\item Packages are {\bf parameterized}, allowing new builds to be composed
      on the fly for different versions, architecture, compiler, options, 
      and dependencies.
\item To manage this large parameter space, spack provides a novel, 
      recursive {\bf spec syntax} for dependency graphs.
\item Specs support versioned, ABI-incompatible interfaces like MPI through
      {\bf versioned virtual dependencies}.
\item Spack builds with {\bf compiler wrappers} that enforce build
      consistency and simplify package writing.
\end{enumerate}

>>>>

%!TEX root = spack-sc15.tex

@@

\noindent
Spack provides the following unique features:
\begin{enumerate}
\item Packages explicitly {\bf parameterized} by version, platform,
      compiler, options, and dependencies, to allow easy composition.
\item A novel, recursive {\bf spec syntax} for dependency graphs and constraints,
      which aids in managing the build parameter space.
\item {\bf Versioned virtual dependencies} to handle versioned, 
      ABI-incompatible interfaces like MPI.
\item A novel {\bf concretization} process that translates an abstract build
      specification into a full, concrete build specification.
\item A build environment with {\bf compiler wrappers} that enforce build
      consistency and simplify package writing.
\end{enumerate}
